### 2018-07-22 express2018/unique.tex
Fixed p6, l-8: "a system of contraction*s*" #10

For a system of contraction, the meaning of 
`solution  for $\rcontr$' and of 
 \emph{a unique 
solution for $\rapprox$}
is the expected one~--- just replace in Definition~\ref{d:uniContra}  the preorder 
$\contr$ with $\rcontr$, and the equivalence 
$\approx$ with $\rapprox$.

>>>>

For a system of contractions, the meaning of 
``solution for $\rcontr$'' and of 
 \emph{a unique 
solution for $\rapprox$}
is the expected one---just replace in Definition~\ref{d:uniContra}  the preorder 
$\contr$ with $\rcontr$, and the equivalence 
$\approx$ with $\rapprox$.
